### 2013-04-10 MSteenhagen-CV.tex
Education label change
Fixed 'department of's

\bigskip
\bigskip
\vfil 
\marginhead{Education \newline (Past)}

\noindent\emph{University College London, Dept. Philosophy \vspace{0.01in}}

@@

\noindent\emph{University of Utrecht, Dept. Philosophy\vspace{0.02in}}

@@

\noindent\emph{ARTeZ School of Fine Art, Dept. Monumental Art\vspace{0.02in}}

@@

\noindent\href{http://www.heythrop.ac.uk/departments/academic-departments/philosophy/}{\emph{Heythrop College London, Dept. Philosophy} \vspace{0.01in}}

@@

\noindent\href{http://www.ucl.ac.uk/philosophy/}{\emph{University College London, Dept. Philosophy}} \vspace{0.01in}

>>>>

\bigskip
\bigskip
\vfil 
\marginhead{Education}

\noindent\emph{University College London, Department of  Philosophy \vspace{0.01in}}

@@

\noindent\emph{University of Utrecht, Department of  Philosophy\vspace{0.02in}}

@@

\noindent\emph{ARTeZ School of Fine Art, Department of Monumental Art\vspace{0.02in}}

@@

\noindent\href{http://www.heythrop.ac.uk/departments/academic-departments/philosophy/}{\emph{Heythrop College London, Department of  Philosophy} \vspace{0.01in}}

@@

\noindent\href{http://www.ucl.ac.uk/philosophy/}{\emph{University College London, Department of  Philosophy}} \vspace{0.01in}
